---
title: "Lab 4 R Version"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readxl)
library(ggthemes)
library(magrittr)
```


```{r}
IndustryTwo<-read_xlsx("Lab4_Files/MSDS6370_LAB04.xlsx")

```

You may use SAS proc means or Excel to calculate the means, sums, and standard deviations required for the allocations in No. 1, 2, 3.

1.  For a sample of size 50 from the population for Industry 2, use proportional allocation to determine the sample size for each of the 5 strata.  Enter these in Table 1 on the Results page.

```{r}
sample_Size = 50
CountsByStrata <- IndustryTwo %>% group_by(stratum) %>% summarise(count=n()) %>% mutate(share=count/sum(count)) %>% mutate(FromThisStratum= round(sample_Size * share, 0))
CountsByStrata

```

2.  For a sample of size 50 from the population for Industry 2, determine the sample size for each of the 5 strata using Neyman allocation where the administrative measure of size of each unit is used in calculating standard deviation for each stratum.  Enter these in Table 2 on the Results page

```{r}
sample_Size = 50
CountsByStrata <- IndustryTwo %>% group_by(stratum) %>% summarise(count=n(), Size = sd(mos)) %>% mutate(share=Size/sum(Size)) %>% mutate(FromThisStratum= round(sample_Size * share, 0))
CountsByStrata

```

3.  For a sample of size 50 from the population for Industry 2, determine the sample size for each of the 5 strata using the sum of the measure of size in stratum h in place of N_h σ_h in a Neyman allocation.  Enter these in Table 3 on the Results page.   



```{r}
sample_Size = 50
CountsByStrata <- IndustryTwo %>% group_by(stratum) %>% summarise(count=n(), Size = sum(mos)) %>% mutate(share=Size/sum(Size)) %>% mutate(FromThisStratum= round(sample_Size * share, 0))
CountsByStrata


```


4. 
(a) Use SAS Procedure Surveyselect to select a sample of size 50 using the proportional allocation to strata as determined in No. 1 above. Output the selected units to a file named propsample. 
```{r}
stratumName<-c(1, 2, 3, 4, 5)
selection<-c(19, 13, 8, 5, 5)

thisStratum <- 1

AllSamples<-data.frame()

for (thisStratum in stratumName) {
  Sampled <-  IndustryTwo %>% filter(stratum == thisStratum) %>% sample_n(selection[thisStratum], replace=FALSE) %>% group_by(stratum) %>% summarise(SampleMean = mean(Sales), SampleSD = sd(Sales))

  AllSamples <- rbind(AllSamples, Sampled)
  
}

```


(b)  Use SAS Procedure Surveymeans and the sample selected using Neyman allocation to form the same estimates in 4 (a).  Enter the estimates from both samples on the Results page.  
```{r}
stratumName<-c(1, 2, 3, 4, 5)
selection<-c(4, 5, 10, 13, 18)

thisStratum <- 1

AllSamples<-data.frame()

for (thisStratum in stratumName) {
  Sampled <-  IndustryTwo %>% filter(stratum == thisStratum) %>% sample_n(selection[thisStratum], replace=FALSE) %>% group_by(stratum) %>% summarise(SampleMean = mean(Sales), SampleSD = sd(Sales))

  AllSamples <- rbind(AllSamples, Sampled)
  
}

```

(C)  Use SAS Procedure Surveymeans and the sample selected using Neyman allocation to form the same estimates in 4 (a).  Enter the estimates from both samples on the Results page.  
```{r}
stratumName<-c(1, 2, 3, 4, 5)
selection<-c(3, 7, 11, 12, 17)

thisStratum <- 1

AllSamples<-data.frame()

for (thisStratum in stratumName) {
  Sampled <-  IndustryTwo %>% filter(stratum == thisStratum) %>% sample_n(selection[thisStratum], replace=FALSE) %>% group_by(stratum) %>% summarise(SampleMean = mean(Sales), SampleSD = sd(Sales))

  AllSamples <- rbind(AllSamples, Sampled)
  
}

```